Transfer Learning in Multimodal Compositional and Relational Reasoning:\\Supplementary Material

### 2019-11-15 cvpr_submission/supplementary_material.tex
Made Supplementary Material its own file.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
%\usepackage{epsfig}
\usepackage{graphicx}
\usepackage[font=small]{subcaption}
\captionsetup[figure]{skip=5pt}
\captionsetup[table]{skip=5pt}
\setlength{\belowcaptionskip}{-15pt}  % reduce padding below figure
\usepackage{amsmath, amssymb, amsfonts,bm}
\usepackage{amsthm}

% Include other packages here, before hyperref.
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{adjustbox}
\usepackage{tabularx}
\usepackage{xcolor}

\usepackage{hyperref}
\hypersetup{
	pagebackref,
	colorlinks,
	breaklinks,
	bookmarks=false,
	linkcolor={red!50!black},
	citecolor={blue!50!black},
	urlcolor={blue!80!black},
	%linkcolor=OliveGreen,
	%citecolor=Blue,
}
%\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{7813} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi

\usepackage{cleveref}
\crefname{section}{Section}{Sections}
\crefname{figure}{Figure}{Figures}
\crefname{table}{Table}{Tables}
\crefname{appendix}{Appendix}{Appendices}
\crefname{definition}{Definition}{Definitions}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{definition}[theorem]{Definition}

\theoremstyle{remark}
\newtheorem*{notation}{Notation}
%\newtheorem*{remark}{Remark}
\newtheorem*{note}{Note}

\newtheorem{fact}{Fact}
\newtheorem*{observation}{Observation}
\newtheorem*{condition}{Condition}
\newtheorem*{claim}{Claim}
\newtheorem*{example}{Example}
\newtheorem*{question}{Question}

\usepackage{enumitem}
\setlist{leftmargin=*}

%% User's macros %%
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\cX}{\mathcal{X}}
\newcommand{\cY}{\mathcal{Y}}
\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\cV}{\mathcal{V}}
\newcommand{\cF}{\mathcal{F}}

\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\vc}{\vec{c}}
\newcommand{\vso}{\vec{so}}
\newcommand{\vone}{\vec{1}}
\newcommand{\proj}{\mathrm{proj}}
\newcommand{\vx}{\vec{x}}
\newcommand{\vy}{\vec{y}}

\newcommand{\imatch}{g^{\mathrm{v}}}
\newcommand{\mmatch}{g^{\mathrm{m}}}

\newcommand{\doadd}{h^{\mathrm{a}}}
\newcommand{\doreplace}{h^{\mathrm{r}}}

\newcommand{\tlast}{\tau^{\mathrm{last}}}
\newcommand{\tlatest}{\tau^{\mathrm{latest}}}
\newcommand{\tnow}{\tau^{\mathrm{now}}}
\newcommand{\tnone}{\tau^{\mathrm{none}}}

\newcommand{\rhead}{\vec{rh}}
\newcommand{\whead}{\vec{wh}}

\newcommand{\uX}{\underline{X}}

\newcommand{\tk}[1]{\textcolor{red}{TK: #1}}
\newcommand{\ao}[1]{\textcolor{green}{AO: #1}}
\newcommand{\tsj}[1]{\textcolor{magenta}{TSJ: #1}}
\newcommand{\vm}[1]{\textcolor{blue}{VM: #1}}

\newcommand{\compresslist}{ % Define a command to reduce spacing within itemize/enumerate environments, this is used right after \begin{enumerate} or \begin{enumerate}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}}

%%%%%%%%%%%%%%%

@@

%%%%%%%%% TITLE
\title{Transfer Learning in Multimodal Compositional and Relational Reasoning}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
  Transfer learning is becoming the de facto solution for vision and text encoders in the front-end processing of machine learning solutions. Utilizing vast amounts of knowledge in pre-trained models and subsequent fine-tuning allows achieving better performance in domains where labeled data is limited. In this paper, we analyze the efficiency of transfer learning in multimodal (vision and language) reasoning by introducing a new model (SAMNet) and testing it on two datasets: COG and CLEVR.  Our new model achieves state-of-the-art accuracy on COG and shows significantly better generalization capabilities compared to the baseline. We also formalize a taxonomy of transfer learning for visual reasoning around three axes: feature, temporal, and reasoning transfer. Based on extensive experimentation on transfer learning on the two datasets, we show the performance of the new model along each axis.
\end{abstract}

%%%%%%%%% BODY TEXT
\input{introduction}

\input{related_work}

\input{transfer_learning}

\input{samnet}

\input{experiments}

\input{summary}

@@

%\clearpage
%\input{appendix}

>>>>

\documentclass[10pt,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{adjustbox}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{url}
\usepackage{enumitem}
\setlist{leftmargin=*}

%\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{7813} 
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\ifcvprfinal\pagestyle{empty}\fi

@@

%%%%%%%%% TITLE
\title{Transfer Learning in Multimodal Compositional and Relational Reasoning:\\Supplementary Material}

@@

\input{appendix}

@@
